%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Developer}                   % Job title
    {Mugonat Systems}   % Organisation
    {}              % Location
    {October 2022 - Present}              % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item
                    {
                        Specialize in web development using frameworks such as Php/Laravel and C\#/ASP.NET for creating custom web applications.
                    }
                    \item
                    {
                        Focused on developing financial systems including a microfinance management platform and an ERP in most recent role.
                    }
                    \item
                    {
                        Required to navigate between the disciplines of software engineering and accounting/bookkeeping and collaborate closely with clients to generate workflows that met their unique accounting requirements and then convert them into effective software solutions.
                    }
                    \item
                    {
                        Experience working on e-commerce sites and completed front-end development work using ReactJS, Vue3, razor pages, jinja, and blade.
                    }
                    \item
                    {
                        Consistently demonstrated ability to deliver high-quality solutions that meet or exceed clients' expectations.
                    }
                    \item
                    {
                        Always seeking to learn new technologies and best practices to stay at the forefront of the industry.
                    }
        \item {\textbf{Technical Skills:} MySQL, PHP/Laravel, C\#/ASP.NET MVC, React.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Critical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Industrial Automation Operator}                   % Job title
    {Newcold Advanced Cold Logistics}   % Organisation
    {}              % Locat
    {June 2022 - Aug 2022}              % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team of three to monitor smooth running of automation in a cold storage facility.}
        \item {Was required to find and resolve system faults which ranged from minor software glitches all the way to damaged mechanical components.}
        \item {In the case the system may be down for a prolonged period, I had to modify operating parameters of the system to optimise system throughput while part of it was down for repairs.}
        \item {Was also required to complete shift reports describing system performance throughout the shift.}
        \item {\textbf{Technical Skills:} Mechanical Aptitude, Electronics, Understanding of PLCs, Understanding of System via Technical Documents, Working at Heights Licence.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Critical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader}           % Job title
    {3rd Party Containers}  % Organisation
    {}  % Location
    {Oct 2017 - May 2022}   % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/3
        \item {Led a team of 3 - 6 team members at a client's site.}
        \item {Regular tasks included: invoicing clients for completed daily tasks, allocating tasks to team members in order to complete daily tasks in a timely and proficient manner, conducting weekly toolbox/safety meetings, enforcing safety directives, liaising with client staff about what needs to get done and how best it can be done in order to minimise cost to the client while producing high quality results, safe forklift operation and manual handling.}
        \item {Was capable of resolving disputes and disruptions among team members when necessary in order to maintain cohesive team.}
        \item {Regularly purchased sundry items such stationary, face masks and safety knives out of my own pocket. I found that this improved team morale and minimised disruptions due to missing equipment.}
        \item {Was the youngest ever appointed team leader on clients site .}
        \item {\textbf{Technical Skills:} Forklift Operation, Safe Manual Handling.}
        \item {\textbf{Soft Skills:} Leadership, Time Management, Communication, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
