%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Systems: IoT Development} % Organisation
    {IoT Mousetrap Network} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {The aim of this project was to develop a network of mouse traps capable of tracking the number of captured mice and synchronizing statistics with a central database. This data can then be processed into meaningful information and presented to users via a web interface.}
        \item {I developed a prototype of the system consisting of one LoraWAN-enabled mousetrap and one LoraWAN gateway. Data storage and processing was facilitated by Thingspeak via The Things Network.}
        \item {\textbf{Technical Skills:} MATLAB, C/C++, python, HTTP/TCP/IP.}
        \item {\textbf{Soft Skills:} Report writing, Critical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\begin{comment}
  \cventry
    {Embedded Systems: RTOS} % Organisation
    {Advanced Traffic Light System using QNX Neutrino} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {We developed a traffic light system with two intersections and a rail level crossing. Each
        intersection had a controller that managed sequences. The railroad was sensor driven.}
        \item {A central controller managed all other controllers. The central controller could override the
        level crossing allowing for manual opening and closing of the boom gates. The central
        controller could also modify the traffic light sequences of each intersection.}
        \item {I was working
        with two other team members.}
        \item {\textbf{Technical Skills:} QNX Neutrino, Git, Discord (For Collaboration).}
        \item {\textbf{Soft Skills:} Critical Thinking, Time Management, Teamwork.}
      \end{cvitems}
    }
\end{comment}


\cventry
            {Web Development: Backend}
		{Loan Management System}
		{}
            {}
		{
                \begin{cvitems}
                    \item 
                    {
                        I am currently undertaking this project under Mugonat Systems. We are developing a Loan Management system for \href{https://panamax.co.zw/}{Panamax Capital (click here)}. I am currently the sole developer on the project and am tasked with performing system design, front-end and back-end duties.
                    }
                    \item
                    {
                        The platform is capable of tracking clients, loans, payroll, creditors and charts of accounting as well as platform user's activity.
                    }
                     \item 
                    {
                        The client is currently making use of the platform in parallel with their traditional record-keeping. We are making use of the minimum viable product principle to continue improving the platform.
                   }
                   \item {\textbf{Technical Skills:} PHP/Laravel, phpMyAdmin, MySql, JavaScript, Vue.}
        \item {\textbf{Soft Skills:} Critical Thinking, Stakeholder engagement.}
                \end{cvitems}
            }
%---------------------------------------------------------
  \cventry
    {Electronics: Circuit \& PCB Design} % Organisation
    {Design and Simulation of a 12-bit RISCV based CPU Architecture and Instruction Set} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {
            The objective of the project was to design a hardware-based CPU architecture and instruction set that could perform calculations for determining the greatest common divisor between two values.
        }
        \item {The circuit was implemented as a PCB using
        Altium designer and each circuit component was soldered to the PCB by hand.}
        \item {\textbf{Technical Skills:} Altium Designer, NI Multism, Soldering Iron, Datasheets.}
        \item {\textbf{Soft Skills:} Critical Thinking, Report Writing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

